Supermartingales and Termination Analysis of Statistical PCF

### 2021-10-01 LICS21/SPCF.tex
Latex minors

\changed[lo]{The one-step reduction of the \emph{trace-based} (or \emph{sampling-style}) \emph{operational semantics} \citep{DBLP:journals/jcss/Kozen81,DBLP:conf/icfp/BorgstromLGS16,DBLP:conf/esop/CulpepperC17}} is given by the function $\red : \Lambda^0 \times \entrosp \to \Lambda^0 \times \entrosp$ where
\begin{equation*}
\red(M,s) := \left\{
    \begin{array}{ll}
        (E[N],s) & \text{if } M = E[R], R \to N\\
        & \qquad \text{ and } R \neq \tsample \\
        (E[\underline{\pi_h(s)}],\pi_t(s)) & \text{if } M = E[\tsample] \\
        (M,s) & \text{if } M \text{ is a value}
    \end{array} \right .
\end{equation*}
%\lo{Both $\to$ and $\red$ are called reduction relation.}

>>>>

\changed[lo]{The one-step reduction of the \emph{trace-based} (or \emph{sampling-style}) \emph{operational semantics} \citep{DBLP:journals/jcss/Kozen81,DBLP:conf/icfp/BorgstromLGS16,DBLP:conf/esop/CulpepperC17}} is given by the function $\red : \Lambda^0 \times \entrosp \to \Lambda^0 \times \entrosp$ where
\begin{equation*}
\red(M,s) := \left\{
    \begin{array}{ll}
        (E[N],s) & \text{if } M = E[R], R \to N \text{ and } R \neq \tsample \\
        (E[\underline{\pi_h(s)}],\pi_t(s)) & \text{if } M = E[\tsample] \\
        (M,s) & \text{if } M \text{ is a value}
    \end{array} \right .
\end{equation*}
%\lo{Both $\to$ and $\red$ are called reduction relation.}
